Treefelling_Sylvain's version

### 2021-12-03 R/Treefelling_Sylvain's version.Rmd
loggingsimulation function and doc refresh
After doc review
ONF modifications

```{r}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016))

@@

  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
    if(dat$TreeFellingOrientationSuccess == "1"){
      A <- st_difference(st_union(
        rotatepolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
        rotatepolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
      ))
      B <- st_difference(st_union(
        rotatepolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
        rotatepolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
      ))
    }else{ # else random felling
      RandomAngle <- sample(c(0:180), size = 1)

@@

  # Fuelwood exploitation in the crowns
  if(fuel =="1" |fuel =="2"){

>>>>

```{r}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)

@@

  # To direct to avoid damage to future and reserve trees + trail orientation. Winching: Foot before.
  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
    if(dat$TreeFellingOrientationSuccess == "1"){
      A <- st_difference(st_union(
        rotatepolygon(Trunk, angle = 240 + theta, fixed = Foot), # turned trunk
        rotatepolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
      ))
      B <- st_difference(st_union(
        rotatepolygon(Trunk, angle = 120 + theta, fixed = Foot), # turned trunk 
        rotatepolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
      ))
    }else{ # else random felling
      RandomAngle <- sample(c(0:180), size = 1)

@@

  # Fuel wood exploitation in the crowns
  if(fuel =="1" |fuel =="2"){
